中国营商环境的地区差异、时空演变与收敛性研究

### 2021-04-19 paper.Rmd
最近更新

---
title: "中国营商环境的地区差异、时空演变与收敛性研究"
subtitle: "Working in Progress"
author: "张沐"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cyanman
    highlight: github
---

@@

<details >
<summary>点击查看雷达图</summary>
```{r echo=F}

```
</details>

@@

moranSC %>% mutate(year = 2010:2019) %>% relocate(3) %>% 
  set_names(c("年份","Moran’s I指数","p值")) %>%
  pivot_longer(-1,names_to = "类型") %>% 
  ggplot(aes(年份,value,color = 类型))+
  scale_colour_ggthemr_d()+
  scale_color_viridis_d()+
  geom_line(size = 1)+
  geom_point(aes(shape = 类型),size = 3)+
  scale_x_continuous(n.breaks = 10)+
  labs(y="",x="年份")+
  geom_hline(yintercept = 0.1,linetype = "dashed")+
  theme(
    text = element_text(family = cnfont),
    plot.margin = margin(20,20,20,20),
    legend.position = "bottom"
  )

>>>>

---
title: "中国营商环境的地区差异、时空演变与收敛性研究"
subtitle: "Working in Progress"
author: "张沐"
date: '`r paste("最近修改日期：",Sys.Date())`'
output:
  prettydoc::html_pretty:
    theme: cyanman
    highlight: github
---

@@

@@

moranSC %>% mutate(year = 2010:2019) %>% relocate(3) %>% 
  set_names(c("年份","Moran’s I指数","p值")) %>% 
  ggplot()+
  geom_point(aes(年份,`Moran’s I指数`),size = 3)+
  geom_line(size = 1,aes(年份,`Moran’s I指数`),color = alpha("red",0.5))+
  geom_text(aes(label = round(`Moran’s I指数`,3),x =年份,y = `Moran’s I指数`),
            nudge_x = 0.05,
            nudge_y = 0.009,color = alpha("red")
            )+
  geom_col(aes(年份,p值),fill = alpha("orange",0.5))+
  scale_x_continuous(n.breaks = 10)+
  labs(y="",x="年份")+
  geom_hline(yintercept = 0.1,linetype = "dashed")+
  geom_hline(yintercept = 0.05,linetype = "dashed")+
  theme(
    text = element_text(family = cnfont),
    plot.margin = margin(20,20,20,20),
    legend.position = "bottom"
  )
```
